Identification and performance of stock-recruitment functions in state

### 2024-02-14 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
correcting slides w/ 3yr projections
i had 10 yr projection for both 3yr and 10yr by mistake

## Projection performance - Relative Error Recruitment (first 3 years)
- Minimal bias (median at most -0.1 for mean SRR)
- Quantile range much larger for BH
 ```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 're.rec.proj.plot_beta_fix.png') )
    ```

@@

@@

>>>>

## Projection performance - Relative Error Recruitment (first 3 years)
- Minimal bias (median at most -0.1 for mean SRR)
- Quantile range much larger for BH
```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 're.rec.proj.plot3yr_beta_fix.png') )
```

@@

```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 're.ssb.proj.plot3yr_beta_fix.png') )
```

@@

```{r,  echo=FALSE, message=FALSE, warnings=FALSE,  out.height='75%', fig.align='center'}
  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'plots_beta_fix', 're.catch.proj.plot3yr_beta_fix.png') )
```
